---
title: "RI COVID-19 Graphs"
output: 
  flexdashboard::flex_dashboard:
    theme: journal
    orientation: columns
    vertical_layout: fill
    favicon: "favicon.ico"
---

```{r setup, include=FALSE}
cases <- readRDS("graphs/cases.rds")
cases100k <- readRDS("graphs/cases100k.rds")
tests <- readRDS("graphs/tests.rds")
pos <- readRDS("graphs/pos.rds")
admissions <- readRDS("graphs/admissions.rds")
hosp <- readRDS("graphs/hosp.rds")
ICU <- readRDS("graphs/ICU.rds")
deaths <- readRDS("graphs/deaths.rds")
vaccinations <- readRDS("graphs/vaccinations.rds")
```

Cases/Testing
===

<center> **RIDOH updates data Monday through Friday in the early afternoon; all weekend data is posted on Mondays.**

**Case/testing data presented with a one-day lag.** </center>

Column {.tabset}
---

### Cases

```{r}
cases
```

### Cases per 100,000

```{r}
cases100k
```

### Tests Performed

```{r}
tests
```

### Test Positivity

```{r}
pos
```

Hospitalizations/Deaths
===

<center>**RIDOH updates data Monday through Friday in the early afternoon; all weekend data is posted on Mondays.**

**Hospital data presented with a two-day lag; death data presented with a one-day lag.**</center>

Column {.tabset}
---

### Hospital Admissions

```{r}
admissions
```

### Currently Hospitalized

```{r}
hosp
```

### ICU/Ventilator

```{r}
ICU
```

### Deaths

```{r}
deaths
```


Vaccine Distribution
=====================================================================


<center> **RIDOH updates data Monday through Friday in the early afternoon; all weekend data is posted on Mondays.**

**Vaccination data presented with a one-day lag.** </center>

### People vaccinated {.no-title}

```{r}
vaccinations
```
